Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-27 qpip0.tex
Remove done author note
More polish

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

Now we try to put together all $i\in [m]$. Define the following quantities:
$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi}$$
$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}$$
$$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
Notice that $z_{ideal}=pz_{true}$ for some probability $p\in[0, 1]$.

>>>>

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

Now we try to put together all $i\in [m]$. First let
$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi}$$
which is the output distribution of $\PiSampZ$.
We also define the following accordingly:
$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}$$
$$z_{ideal}\defeq \frac{1}{m}\sum_i z_{ideal,i}$$
Notice that $z_{ideal}$ is some ideal output distribution, which (a priori) might not have the same accept probability as $z$.
